\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}
\begin{center}\textbf{Acknowledgements}\end{center}

This thesis would not have been possible if not for my interactions with a few key people.
Most notably, my advisor, Chris Eliasmith, who gave me the freedom to swim into the deep end, and the structure, inspiration, counsel, and courage, to ask difficult, but relevant, questions.
Next, comes Terry Stewart, who programmed the Nengo backend for Braindrop, and has been an invaluable source of insight when it comes to his technical prowess, breadth of knowledge, and intuition behind constructing functional spiking networks using Nengo.
In my earlier days, Trevor Bekolay, Travis DeWolf, Daniel Rasmussen, and Xuan Choo, all played critical roles in my upbringing, by engaging with my exploration into the Neural Engineering Framework and Nengo.
Also, Eric Hunsberger, Jan Gosmann, Peter Duggins, and Andreas St{\"o}ckel, have each given feedback and provided foundational research that has deeply influenced my work.

Special mention must go out to Kwabena Boahen, who, thoughout every one of our interactions, has indescribably imparted invaluable streams of insight in his critical and uncompromising quest for answers.
Many of his questions, contributions, and comments on papers, have inevitably influenced large portions of this thesis in a positive but subtly-pervasive manner.
This extends to memorable moments with all of his students, but especially Sam Fok, Alex Neckar, and Eric Kauderer-Abrams -- these collaborations have been a privilege.

Briefly speaking with Mike Davies, hearing his eloquent characterization of neuromorphic computing, and having his genuine support in getting Loihi into the hands of researchers, has all been integral to propelling this work.
Wilten Nicola has provided a few influential communications on double-exponential synapses and FORCE learning, while Jamie Knight and Michael Hopkins have each provided important references involving SpiNNaker and high-dimensional sampling.
The words of many others have shaped this thesis throughout.

At the institutional level, I would like to acknowledge the support that I've received from
ABR (for Nengo and NengoLib development and experimentation with Loihi),
Intel (for access to Loihi),
Femtosense (for access to and support with Braindrop),
and the University of Manchester (for access to SpiNNaker).
Likewise, my acceptance into the neuromorphic workshops of Telluride, Capo Caccia, Intel's Neuromorphic Research Community~(INRC), and the Nengo Summer School, have all proven to be constructive experiences and motivational fuel.
The Centre for Theoretical Neuroscience~(CTN), Computational Neuroscience Research Group~(CNRG), David R. Cheriton School of Computer Science, and the University of Waterloo, have all contributed to providing a supportive academic environment over the past 11 years.  

\newpage

The experiments throughout this thesis make extensive use of Python, NumPy, SciPy, Jupyter, Matplotlib, Seaborn, Pandas, Nengo, Hyperopt, Scitkit-learn, Keras, and Tensorflow -- for this, we are incredibly grateful to its thousands of contributors.
\TODO{Make sure to cite the primary publications for each of these libraries in methods section.}
A repeated mention is in order for Trevor, who provided this \LaTeX{} template and facilitated my contributions to the Nengo software ecosystem.
Likewise, Daniel, Eric, and Jan, for their help with Nengo development, provisioning of useful code, and feedback.

Working backwards in time, I would also like to thank Mani Fazeli for his many letters of support and words of wisdom at the start of graduate school, as well as Carol Norman for her recurring words of encouragement leading up.
And the enriched education that I received from my teacher Jon Devlin, at Bell High School, was monumental in my decision to study computer science at the University of Waterloo.

At a personal level, Chris has been an outstanding role model for how to live a balanced and meaningful life, as an academic, parent, and human being, all in ways that I can only aspire towards.
Jason Batten-Carew has been the source of many extended philisophical discussions centered about the nature of reality, perception, stories, games, and cycles, all of which have undoubtedly rooted their way into my most basic pursuits for meaning.
I also thank my Mom and Dad for exciting my curiosity, and enabling my studies, throughout my entire life.
And finally, my wife, for providing much-needed perspective and support throughout it all.

\cleardoublepage
